---
title: "Additional MLR on nonzero dataset"
author: "Gulzina Kuttubekova, Meltem Ozcan"
date: "12/6/2019"
output: pdf_document
---


```{r, include=FALSE}
library(dplyr)
library(ggplot2)
library(reshape)
library(gdata)
library(RColorBrewer)
library(visdat)
library(naniar)
library(inspectdf)
library(corrplot)
library(splitstackshape)
library(lmtest)
```


```{r}
games <- read.csv('games.csv')
sales <- read.csv('sales.csv')
```

```{r}
# filter zero sales out
sales <- sales %>% select_all() %>% filter(Sales != 0)
```

```{r}
set.seed(13)
sets <- stratified(sales, c('Platform', 'Genre', 'Publisher',
                            'Developer', 'Rating', 'Decade',
                            'Platform_Company', 'Platform_Gen',
                            'Family_Platform', 'Main_Developer',
                            'Developer_Country', 'Main_Publisher',
                            'Region'), 0.7, bothSets = TRUE)

train_sales <- sets$SAMP1
test_sales <- sets$SAMP2
```


# MLR 3 - on the dataset without zeros, interactions are kept
```{r}
mlr3_nonzero <- lm(log(Sales) ~ Region + Genre + Rating + 
               Critic_Score + Platform_Gen +
               Region:Genre, data = train_sales)
mlr3_nonzero %>% summary()
```

```{r}
anova(mlr3_nonzero)
```
 
We observed the same trend on assumptions violations! We'll check all possible model assessments at the end. 




# MLR 4 - on the dataset without zeros, interactions are kept
```{r}
mlr4_nonzero <- lm(log(Sales) ~ Region + Genre + Rating + 
               Main_Publisher + Platform_Gen +
               Region:Genre + Region:Main_Publisher, data = train_sales)
mlr4_nonzero %>% summary()
```

```{r}
anova(mlr4_nonzero)
```
 AdjR6 dropped significantly!!!

We observed the same trend on assumptions violations! We'll check all possible model assessments at the end. 






# MLR 5
```{r}
mlr5_nonzero <- lm(log(Sales) ~ Region + Genre + Rating + 
               Main_Developer + Platform_Company +
               Region:Genre + Region:Main_Developer, data = train_sales)
mlr5_nonzero %>% summary()
```

```{r}
anova(mlr5_nonzero)
```
 Still all 5 variables including the interactions are significant. Adj-R^2 is 0.4094, dropped from mlr3 and mlr4. Model violations are the same.






# MLR 6
```{r}
mlr6_nonzero <- lm(log(Sales) ~ Region + Genre + Rating + Region:Genre, 
           data = train_sales)
mlr6_nonzero %>% summary()
```

```{r}
anova(mlr6_nonzero)
```
 Still all 3 variables including the interactions are significant. Adj-R^2 is really badddd, decreased from all previous cases. Model violations are the same.

We observed the same trend on assumptions violations! We'll check all possible model assessments at the end. 


# Model Comparison


Predictions and RMSE:
```{r}
# rmse on train data
sqrt(sum((mlr3_nonzero$fitted.values - train_sales$Sales)^2) / length(mlr3_nonzero$fitted.values))


predicted_sales <- predict(mlr3_nonzero, test_sales[,c(3,5,10,14,19)])

# rmse on test data
sqrt(sum((predicted_sales - test_sales$Sales)^2) / length(predicted_sales))
```


```{r}
# rmse on train data
sqrt(sum((mlr4_nonzero$fitted.values - train_sales$Sales)^2) / length(mlr4_nonzero$fitted.values))


predicted_sales <- predict(mlr4_nonzero, test_sales[,c(3,10,14,18,19)])

# rmse on test data
sqrt(sum((predicted_sales - test_sales$Sales)^2) / length(predicted_sales))
```


```{r}
# rmse on train data
sqrt(sum((mlr5_nonzero$fitted.values - train_sales$Sales)^2) / length(mlr5_nonzero$fitted.values))


predicted_sales <- predict(mlr5_nonzero, test_sales[,c(3, 10, 16, 13, 19)])

# rmse on test data
sqrt(sum((predicted_sales - test_sales$Sales)^2) / length(predicted_sales))
```


```{r}
# rmse on train data
sqrt(sum((mlr6_nonzero$fitted.values - train_sales$Sales)^2) / length(mlr6_nonzero$fitted.values))


predicted_sales <- predict(mlr6_nonzero, test_sales[,c(3, 10, 19)])

# rmse on test data
sqrt(sum((predicted_sales - test_sales$Sales)^2) / length(predicted_sales))
```


Create dataframe for model assessment:
```{r}
df <- data.frame(AIC = c(AIC(mlr3_nonzero), AIC(mlr4_nonzero), 
                         AIC(mlr5_nonzero), AIC(mlr6_nonzero)),
                 BIC = c(BIC(mlr3_nonzero), BIC(mlr4_nonzero),
                         BIC(mlr5_nonzero), BIC(mlr6_nonzero)),
                 AdjRsq = c(0.3097, 0.2877, 0.2795, 0.1949),
                 trainRMSE = c(2.890188, 2.886228, 2.886106, 2.875492),
                 testRMSE = c(2.837222, 2.951015, 2.929614, 2.986754))
row.names(df) <- c('MLR3_nonzero', 'MLR4_nonzero', 
                   'MLR5_nonzero', 'MLR6_nonzero')
df
```





