---
title: "ANOVA_no_zero"
author: "Gulzina Kuttubekova, Meltem Ozcans"
date: "12/5/2019"
output: pdf_document
---

```{r, include=FALSE}
library(dplyr)
library(ggplot2)
library(reshape)
library(gdata)
library(RColorBrewer)
library(visdat)
library(naniar)
library(inspectdf)
library(corrplot)
library(splitstackshape)
library(lmtest)
```


```{r}
games <- read.csv('games.csv')
sales <- read.csv('sales.csv')
```

```{r}
# log-transform and remove zeros
sales_nonzero <- sales %>% select_all() %>% 
    filter(Sales != 0) 
```


# Hypothesis 1:
```{r}
genre_region <- lm(log(Sales) ~ Genre*Region, data = sales_nonzero)
genre_region %>% anova()
```

Check the assumptions:
```{r}
plot(genre_region)
```

Based on the QQ plot and residual plot there isn't much deviation from the normality and homogenity assumptions. There appears to be a small pattern in residual plot, we will check if it's significant by additional tests:
```{r}
shapiro.test(genre_region$residuals
             [sample(1:length(sales_nonzero$Platform), 5000)])
```

We see that the normality assumption is actually violated. What about homogeneity? - It's also violated!!! There are no outliers and influential points.
```{r}
bptest(genre_region)
```

WLS method might be a potential remedy for the assumptions violations. So try this:
```{r}
varfunc_gen_reg <- lm(log(genre_region$residuals^2) ~ Genre*Region, 
                      data = sales_nonzero)
sales_nonzero$varfunc_gen_reg <- exp(varfunc_gen_reg$fitted.values)
genre_region_gls <- lm(log(Sales) ~ Genre*Region, 
                       weights = 1/sqrt(varfunc_gen_reg),
                       data = sales_nonzero)
```

Check normality:
```{r}
shapiro.test(genre_region_gls$residuals
             [sample(1:length(sales_nonzero$Platform), 5000)])
```

P-value had increased from previous LS case, but still is less than 0.05. Hence WLS method didn't help to resolve the abnormality :D issue.

```{r}
bptest(genre_region_gls)
```

Homogeneity is also still violated!!!







# Hypothesis 2:
```{r}
dev_region <- lm(log(Sales) ~ Main_Developer*Region, data = sales_nonzero)
dev_region %>% anova()
```

Check the assumptions:
```{r}
plot(dev_region)
```

Based on the QQ plot and residual plot there isn't much deviation from the normality and homogenity assumptions. There appears to be a small pattern in residual plot, we will check if it's significant by additional tests:
```{r}
shapiro.test(dev_region$residuals
             [sample(1:length(sales_nonzero$Platform), 5000)])
```

We see that the normality assumption is actually violated. What about homogeneity? - It's also violated!!! There are no outliers and influential points.
```{r}
bptest(dev_region)
```

WLS method might be a potential remedy for the assumptions violations. So try this:
```{r}
varfunc_dev_reg <- lm(log(dev_region$residuals^2) ~ Main_Developer*Region, 
                      data = sales_nonzero)
sales_nonzero$varfunc_dev_reg <- exp(varfunc_dev_reg$fitted.values)
dev_region_gls <- lm(log(Sales) ~ Main_Developer*Region, 
                       weights = 1/sqrt(varfunc_dev_reg),
                       data = sales_nonzero)
```

Check normality:
```{r}
shapiro.test(dev_region_gls$residuals
             [sample(1:length(sales_nonzero$Platform), 5000)])
```

P-value is strictly less than 0.05 -- reject the null hypothesis stating the normality of residuals! NOT normal!!!! Hence WLS method didn't help to resolve the abnormality :D issue.

```{r}
bptest(dev_region_gls)
```

Homogeneity is also still violated!!!





# Hypothesis 3

```{r}
pub_region <- lm(log(Sales) ~ Main_Publisher*Region, data = sales_nonzero)
pub_region %>% anova()
```

Check the assumptions:
```{r}
plot(pub_region)
```

Based on the QQ plot and residual plot there isn't much deviation from the normality and homogenity assumptions. There appears to be a small pattern in residual plot, we will check if it's significant by additional tests:
```{r}
shapiro.test(pub_region$residuals
             [sample(1:length(sales_nonzero$Platform), 5000)])
```

We see that the normality assumption is actually violated. What about homogeneity? - It's also violated!!! There are no outliers and influential points.
```{r}
bptest(pub_region)
```

WLS method might be a potential remedy for the assumptions violations. So try this:
```{r}
varfunc_pub_reg <- lm(log(pub_region$residuals^2) ~ Main_Publisher*Region, 
                      data = sales_nonzero)
sales_nonzero$varfunc_pub_reg <- exp(varfunc_pub_reg$fitted.values)
pub_region_gls <- lm(log(Sales) ~ Main_Publisher*Region, 
                       weights = 1/sqrt(varfunc_pub_reg),
                       data = sales_nonzero)
```

Check normality:
```{r}
shapiro.test(pub_region_gls$residuals
             [sample(1:length(sales_nonzero$Platform), 5000)])
```


P-value has increased but still strictly less than 0.05 -- reject the null hypothesis stating the normality of residuals! NOT normal!!!! Hence WLS method didn't help to resolve the abnormality :D issue.

```{r}
bptest(pub_region_gls)
```

Homogeneity is also still violated!!!




# Hypothesis 4


```{r}
gen_dec <- lm(log(Sales) ~ Genre*Decade, data = sales_nonzero)
gen_dec %>% anova()
```

Check the assumptions:
```{r}
plot(gen_dec)
```

Based on the QQ plot and residual plot there isn't much deviation from the normality and homogenity assumptions. There appears to be a small pattern in residual plot, we will check if it's significant by additional tests:
```{r}
shapiro.test(gen_dec$residuals
             [sample(1:length(sales_nonzero$Platform), 5000)])
```

We see that the normality assumption is actually violated. What about homogeneity? - It's also violated!!! There are no outliers and influential points.
```{r}
bptest(gen_dec)
```

WLS method might be a potential remedy for the assumptions violations. So try this:
```{r}
varfunc_gen_dec <- lm(log(gen_dec$residuals^2) ~ Genre*Decade, 
                      data = sales_nonzero)
sales_nonzero$varfunc_gen_dec <- exp(varfunc_gen_dec$fitted.values)
gen_dec_gls <- lm(log(Sales) ~ Genre*Decade, 
                       weights = 1/sqrt(varfunc_gen_dec),
                       data = sales_nonzero)
```

Check normality:
```{r}
shapiro.test(gen_dec_gls$residuals
             [sample(1:length(sales_nonzero$Platform), 5000)])
```


P-value is strictly less than 0.05 -- reject the null hypothesis stating the normality of residuals! NOT normal!!!! Hence WLS method didn't help to resolve the abnormality :D issue.

```{r}
bptest(gen_dec_gls)
```

Homogeneity is also still violated!!!










