---
title: "Exploratory and Preliminary Data Analysis of Rideshare dataset"
author: "Gulzina Kuttubekova & Meltem Ozcan"
date: "11/2/2019"
output: pdf_document
---

```{r, include=FALSE}
library(dplyr)
library(ggplot2)
library(reshape)
library(gdata)
```



### Data:
- Where did we get it? 
    Data can be downloaded here: [Kaggle](https://www.kaggle.com/kendallgillies/video-game-sales-and-ratings)
    
- How it was collected?
    <This data set contains a list of video games with sales greater than 100,000 copies along with critic and user ratings. It is a combined web scrape from `VGChartz` and `Metacritic` along with manually entered year of release values for most games with a missing year of release>. It contains game sales information starting from 

- By whom? 
    References: Rush Kirubi, Gregory Smith and Kendall Gillies



#### Data summary:
```{r}
games <- read.csv('data/Video_Games_Sales_as_at_22_Dec_2016.csv',
                  header = TRUE , na.strings=c("", " ", "N/A", "NA"))
games %>% glimpse()
```

```{r, include=FALSE}
# convert User_Count to numerical variable
games$User_Score <- as.numeric(as.character(games$User_Score))
```

There are 16,719 instances observed with 16 variables. There are 5 categorical: {Name, Platform, Genre, Publisher, Developer} and 10 numerical: {Year, NA_Sales, EU_Sales, JP_Sales, Other_Sales, Global_Sales, Critic_Score, Critic_Count, User_Score, User_Count, Rating} variables. 


```{r}
describe <- function(var) {
# This function summarizes each variable. It prints out descriptive sample 
# statistics for numerical variables, and contingency table for categorical 
# variables.  
#     
# Args:
#   var: variable in a vector form
#    
# Returns:
#   Summary analysis
    if (is.numeric(var)) {
        summary(var)
    }
        
    else if (is.factor(var)) {
        if (length(unique(var)) > 40) {
            sprintf('There are %d unique cases', length(unique(var)))
        } else {
            table(var)
        }
    }
}
```


`describe()` function applied on each variable in Games dataset, outputs the following result:
```{r}
lapply(games, describe)
```

```{r}
# the same analysis with summary function()
games %>% summary()
```

According to the output, there are total 1697 unique developers, and 582 unique pusblishers. Top 3 most popular platforms are *PS2*, *DS* and *PS3*. Top 3 most popular genres are *Action*, *Sports* and *Miscallenous*. The average sales in North America is \$263k, while in Europe it's \$145k, \$78k in Japan and $47k in other parts of the world. The average global sales resulted in \$534k. 

```{r}
# Write a function to calculate NA's or missing values
count_NAs <- function(var) {
# Counts missing values in each variable
#
# Args:
#   var: variable in a vector form
#
# Returns:
#   Number of missing values in each variable
    sprintf('There are %d missing values', sum(is.na(var)))
}
```

```{r}
lapply(games, count_NAs)
```

There are many missing values almost in every variable. For instance, there are 269 observations with unknown release date. Also, there are massive missing values in the variables like Critic_Score, Critic_Count, User_Score, User_Count, Developer and Rating. **Since most of the missing values are in categorical variables**, we can't just replace/fill, so we will drop/omit those missing values.





#### Data cleaning/manipulation:
```{r}
games <- na.omit(games)
games %>% glimpse()
```

```{r}
games %>% summary()
```

After removing all NA cases, we were left with 6947 observations. Hence we lost %58.44 of inital observations. 


For more flexibility we can generate new variables out of given 16. Below are given the mechanisms we used to generate those additional features:

Write the reasoning here why do we need this KPI/variable?

1. Year since release: numeric variable
```{r}
games$Year_since_Release <- max(games$Year_of_Release) - games$Year_of_Release
```




2. Year to decade categorical
```{r}
to_decade <- function(var) {
    var[var <= 1980] <- '70s'
    var[1980 < var & var <= 1990] <- '80s'
    var[1990 < var & var <= 2000] <- '90s'
    var[2000 < var & var <= 2010] <- '00s'
    var[2010 < var & var <= 2020] <- '10s'
    
    return(var)
}
```

```{r}
games$Decade <- to_decade(games$Year_of_Release)
```





3. Platform Developer company

```{r}
platform_company <- function(var) {
    var <- as.character(var)
    
    var[var == "3DS"|
        var == "DS"|
        var == "GBA"|
        var == "GC"|
        var == "Wii"|
        var == "WiiU"] = 'Nintendo'
    var[var == "DC"] = 'Sega'
    var[var == "PC"|
        var == "X360"|
        var == "XB"|
        var == "XOne"] = 'Microsoft'
    var[var == "PS"|
        var == "PS2"|
        var == "PS3"|
        var == "PS4"|
        var == "PSP"|
        var == "PSV"] = 'SONY'
    
    return(var)
}
```

```{r}
games$Platform_Company <- platform_company(games$Platform)
```





4. Platforms Generation

Create new variable by generation of platforms:
```{r}
platforms_gen <- function(var) {
    var = as.character(var)
    
    var[var == "PS" | 
        var == "PC"] = 'Fifth Gen'
    var[var == "DC" | 
        var == "PS2" | 
        var == "XB" | 
        var == "GBA" | 
        var == "GC"] = 'Sixth Gen'
    var[var == "DS" | 
        var == "PS3" | 
        var == "PSP" |
        var == "Wii" |
        var == "X360"] = 'Seventh Gen'
    var[var == "3DS" | 
        var == "PS4" | 
        var == "PSV" | 
        var == "WiiU" | 
        var == "XOne"] = 'Eigth Gen'
    
    return(var)
}
```

```{r}
games$Platform_Gen <- platforms_gen(games$Platform)
```





5. Variable by family of systems
```{r}
family_platforms <- function(var) {
    var = as.character(var)
    
    var[var == "3DS" |
        var ==  "DS"] = 'Nintendo_DS'
    var[var == "DC" | 
        var == "PC" | 
        var == "GBA" | 
        var == "GC"] = 'Misc'
    var[var == "X360" |
        var == "XB" |
        var == "XOne"] = 'Microsoft_XBOX'
    var[var == "PS" |
        var == "PS2" |
        var == "PS3" | 
        var == "PS4" |
        var == "PSP" |
        var == "PSV"] = 'SONY_PS'
    var[var == "Wii" |
        var == "WiiU"] = 'Nintendo_Wii'
    
    return(var)
}
```

```{r}
games$Family_Platform <- family_platforms(games$Platform)
```





6. Developer (publisher) country information
```{r}
developer_countries <- read.xls('data/Country_data.xlsx', header = TRUE)
developer_countries %>% glimpse()
```

```{r}
developer_countries %>% head()
```

Link this information to the developer variable: (we will actually refer to the top 10 largest video game developer companies in the world):
```{r}
filter_developer <- function(var, ids = as.numeric(rownames(games))) {
    var <- as.character(var)
    
    var[grepl('Ubisoft', var)] <- 'Ubisoft'
    var[grepl('Vivendi', var)] <- 'Ubisoft'
    var[grepl('Ivory Tower', var)] <- 'Ubisoft'
    var[grepl('Massive Entertainment', var)] <- 'Ubisoft'
    var[grepl('Nadeo', var)] <- 'Ubisoft'
    var[grepl('Red Storm', var)] <- 'Ubisoft'
    var[grepl('RedLynx', var)] <- 'Ubisoft'
    var[grepl('Microids', var)] <- 'Ubisoft'
    var[grepl('Related Designs', var)] <- 'Ubisoft'
    var[grepl('Sunflowers Interactive', var)] <- 'Ubisoft'
    var[ids %in% c(2585, 6804)] <- 'Ubisoft' #games developed by Marvelous
    var[ids == 3227] <- 'Ubisoft' #game developed by Media Vision
    var[ids %in% c(4455, 7097, 7213)] <- 'Ubisoft' #games developed by Q entertainment
    var[ids %in% c(8816, 11234)] <- 'Ubisoft' #games developed by Racjin
    var[ids == 5039] <- 'Ubisoft' #games by Yuke's
    var[ids == 11246] <- 'Ubisoft'
    var[ids %in% c(12158, 14003)] <- 'Ubisoft' #Climax
    var[ids %in% c(9025, 9794)] <- 'Ubisoft' #Kuju
    var[ids == 6900] <- 'Ubisoft' #Sumo
    var[ids %in% c(3133, 4934, 5181, 6076, 6685, 7700, 7998,
                   9135, 9945, 10701, 11164, 14849)] <- 'Ubisoft' #Eurocom

    
    var[grepl('Nintendo', var)] <- 'Nintendo'
    var[grepl('Monolith Soft', var)] <- 'Nintendo'
    var[grepl('Retro Studios', var)] <- 'Nintendo'
    var[grepl('Ambrella', var)] <- 'Nintendo'
    var[grepl('Camelot Software Planning', var)] <- 'Nintendo'
    var[grepl('Creatures', var)] <- 'Nintendo'
    var[grepl('Game Freak', var)] <- 'Nintendo'
    var[grepl('Creatures', var)] <- 'Nintendo'
    var[grepl('Genius Sonority', var)] <- 'Nintendo'
    var[grepl('Good-Feel', var)] <- 'Nintendo'
    var[grepl('HAL', var)] <- 'Nintendo'
    var[grepl('Intelligent Systems', var)] <- 'Nintendo'
    var[grepl('Next Level Games', var)] <- 'Nintendo'
    var[grepl('Sora', var)] <- 'Nintendo'
    var[grepl('TOSE', var)] <- 'Nintendo'
    var[ids %in% c(313, 554, 730)] <- 'Nintendo' #games developed by Capcom
    var[ids %in% c(4121, 4619)] <- 'Nintendo' #games developed by Marvelous
    var[ids == 6984 ] <- 'Nintendo' #game developed by Q Entertainment
    var[ids == 6309] <- 'Nintendo' #FreeStyleGame
    var[ids %in% c(4789, 5367)] <- 'Nintendo' #Kuju
    var[ids %in% c(545, 3098, 3109, 4184)] <- 'Nintendo' #Artoon
    var[grepl('n-Space', var)] <- 'Nintendo'
    
    
    var[grepl('SONY', var)] <- 'SONY'
    var[grepl('Sony', var)] <- 'SONY'
    var[grepl('SCE', var)] <- 'SONY'
    var[grepl('SIE', var)] <- 'SONY'
    var[grepl('Bend', var)] <- 'SONY'
    var[grepl('Insomniac', var)] <- 'SONY'
    var[grepl('Media Molecule', var)] <- 'SONY'
    var[grepl('Naughty Dog', var)] <- 'SONY'
    var[grepl('Polyphony', var)] <- 'SONY'
    var[grepl('Sucker', var)] <- 'SONY'
    var[grepl('Bigbig', var)] <- 'SONY'
    var[grepl('Evolution', var)] <- 'SONY'
    var[grepl('Guerrilla', var)] <- 'SONY'
    var[grepl('Incognito', var)] <- 'SONY'
    var[grepl('Liverpool', var)] <- 'SONY'
    var[grepl('Zipper', var)] <- 'SONY'
    var[grepl('Clap Hanz', var)] <- 'SONY'
    var[ids == 8837] <- 'SONY' #ALfa Systems, Oreshika game
    var[ids == 3087] <- 'SONY' #Dimps, Japan Studio
    var[ids == 7065] <- 'SONY' #Matrix Systems, Alundra game
    var[ids == 10967] <- 'SONY' #Media Vision, Wild Arms
    var[ids ==5456] <- 'SONY' #Shift, Ape Academy
    var[grepl('Zener', var)] <- 'SONY'
    var[grepl('Bluepoint', var)] <- 'SONY'
    var[ids %in% c(4515, 7818, 8028)] <- 'SONY' #Harmonix
    var[ids %in% c(3291, 4257, 9503)] <- 'SONY' #High Impact Games
    var[grepl('Idol', var)] <- 'SONY'
    var[grepl('Magic Pixel', var)] <- 'SONY'
    #var[ids == 3885] <- 'SONY' #Mass Media
    var[grepl('Ready to Dawn', var)] <- 'SONY'
    var[ids %in% c(2979, 3341, 3680, 6765, 7509)] <- 'SONY' #Sanzaru Games
    var[ids == 9843] <- 'SONY' #SuperVillain
    var[grepl('Workshop', var)] <- 'SONY'
    var[grepl('Zindagi', var)] <- 'SONY'
    var[ids == 8802] <- 'SONY' #Climax
    var[ids == 1596] <- 'SONY' #Double Eleven
    var[ids == 13343] <- 'SONY' #FreeStyleGames
    var[ids == 4560] <- 'SONY' #Frontier
    #var[ids == 1115] <- 'SONY' #Ninja
    var[ids == 909] <- 'SONY' #Sumo
    var[ids %in% c(464, 1128)] <- 'SONY' #Quantic
    var[grepl('989', var)] <- 'SONY'
    var[grepl('Cohort', var)] <- 'SONY'
    var[ids %in% c(2720, 5647, 7043)] <- 'SONY' #Game Republic
    var[grepl('BottleRocket', var)] <- 'SONY'
    var[ids %in% c(396, 6284, 8263)] <- 'SONY' #Eurocom
    var[ids %in% c(8291, 4746)] <- 'SONY' #Nihilistic
    var[ids %in% c(1588, 4428)] <- 'SONY' #Slant Six
    var[grepl('SuperBot', var)] <- 'SONY'
    var[ids %in% c(1823, 2394)] <- 'SONY' #UnitedFrontGames
    var[grepl('Level 5', var)] <- 'SONY'
    
    
    var[grepl('EA', var)] <- 'EA'
    var[grepl('Electronic Arts', var)] <- 'EA'
    var[grepl('DICE', var)] <- 'EA'
    var[grepl('Ghost Games', var)] <- 'EA'
    var[grepl('PopCap', var)] <- 'EA'
    var[grepl('BioWare', var)] <- 'EA'
    var[grepl('Frostbite', var)] <- 'EA'
    var[ids == 1423] <- 'EA' #developed by Bluepoint
    #var[ids %in% c(2119, 2201)] <- 'EA' #developed by Double Fine
    var[ids == 740] <- 'EA' #developed by Harmonix
    var[ids == 9777] <- 'EA' #developed by Sanzaru Games
    var[grepl('Exient', var)] <- 'EA'
    var[grepl('Maxis', var)] <- 'EA'
    var[grepl('Black Box', var)] <- 'EA'
    var[ids == 16314] <- 'EA' #Kuju
    var[ids %in% c(405, 859, 2504, 2636, 2959, 3592, 4188,
                   5235, 7435, 8924)] <- 'EA' #Eurocom
    var[ids %in% c(6116, 4992, 2650)] <- 'EA' #Nihilistic

    
    var[grepl('Microsoft', var)] <- 'Microsoft'
    var[grepl('343', var)] <- 'Microsoft'
    var[grepl('Compulsion', var)] <- 'Microsoft'
    var[grepl('Double Fine', var)] <- 'Microsoft'
    var[grepl('Ninja Theory', var)] <- 'Microsoft'
    var[grepl('Obsidian', var)] <- 'Microsoft'
    var[grepl('Playground', var)] <- 'Microsoft'
    var[grepl('Rare', var)] <- 'Microsoft'
    var[grepl('Coalition', var)] <- 'Microsoft'
    var[grepl('Turn', var)] <- 'Microsoft'
    var[grepl('Indie', var)] <- 'Microsoft'
    var[grepl('Bungie', var)] <- 'Microsoft'
    var[grepl('Twisted', var)] <- 'Microsoft'
    var[grepl('BigPark', var)] <- 'Microsoft'
    var[grepl('Anvil', var)] <- 'Microsoft'
    var[grepl('Ensemble', var)] <- 'Microsoft'
    var[grepl('FASA', var)] <- 'Microsoft'
    var[grepl('Good Science', var)] <- 'Microsoft'
    var[grepl('Lionhead', var)] <- 'Microsoft'
    var[ids == 1177] <- 'Microsoft'
    var[ids == 10678] <- 'Microsoft' #developed by Media Vision
    var[ids == 8981] <- 'Microsoft' #developed by Armature
    var[ids %in% c(838, 2526, 7960)] <- 'Microsoft' #developed by Harmonix
    var[ids %in% c(15061, 7826)] <- 'Microsoft' #developed by Climax
    var[ids %in% c(676, 1138)] <- 'Microsoft' #developed by Frontier
    var[ids == 13474] <- 'Microsoft' #Kuju
    var[ids %in% c(2263, 3600, 7434)] <- 'Microsoft' #Artoon
    var[ids == 1653] <- 'Microsoft' #Blitz
    
    
    var[grepl('Epic Games', var)] <- 'Tencent'
    var[grepl('Paradox', var)] <- 'Tencent'
    
    
    var[grepl('Activision', var)] <- 'Activision Blizzard'
    var[grepl('Blizzard', var)] <- 'Activision Blizzard'
    var[grepl('Vicarious Visions', var)] <- 'Activision Blizzard'
    var[grepl('Treyarch', var)] <- 'Activision Blizzard'
    var[grepl('Beenox', var)] <- 'Activision Blizzard'
    
    
    var[grepl('Namco', var)] <- 'Namco'
    var[grepl('Bandai', var)] <- 'Namco'
    var[grepl('Telenet', var)] <- 'Namco'
    var[grepl('Atari', var)] <- 'Namco'
    
    
    var[grepl('GungHo', var)] <- 'GungHo'
    var[grepl('Game Arts', var)] <- 'GungHo'
    var[grepl('Interchannel', var)] <- 'GungHo'
    var[grepl('Grasshopper', var)] <- 'GungHo'
    var[grepl('Acquire', var)] <- 'GungHo'
    
    
    var[grepl('TT', var)] <- 'Warner Brothers'
    var[grepl('Tales', var)] <- 'Warner Brothers'
    var[grepl('Giants', var)] <- 'Warner Brothers'
    var[grepl('Tales', var)] <- 'Warner Brothers'
    var[grepl('Warthog', var)] <- 'Warner Brothers'
    var[grepl('Avalanche', var)] <- 'Warner Brothers'
    var[grepl('Monolith Productions', var)] <- 'Warner Brothers'
    var[grepl('NetherRealm', var)] <- 'Warner Brothers'
    var[grepl('Rocksteady', var)] <- 'Warner Brothers'
    var[grepl('WB', var)] <- 'Warner Brothers'
    var[grepl('Midway', var)] <- 'Warner Brothers'
    var[grepl('Eidos', var)] <- 'Warner Brothers'
    var[grepl('Turbine', var)] <- 'Warner Brothers'
    
    
    var[grepl('Square', var)] <- 'Square Enix'
    var[grepl('Taito', var)] <- 'Square Enix'
    var[grepl('Tri-Ace', var)] <- 'Square Enix'
    
    
    var[grepl('Visual Concepts', var)] <- 'Sega'
    var[grepl('Sega', var)] <- 'Sega'
    var[grepl('2K', var)] <- 'Sega'
    var[grepl('Take-Two', var)] <- 'Sega'
    var[grepl('Sonic', var)] <- 'Sega'
    var[grepl('Kush', var)] <- 'Sega'
    
    
    var[grepl('Volition Inc', var)] <- 'THQ'
    var[grepl('THQ', var)] <- 'THQ'
    var[grepl('Deep Silver', var)] <- 'THQ'
    var[grepl('Pacific Coast', var)] <- 'THQ'
    var[grepl('Relic', var)] <- 'THQ'
    var[grepl('Vigil', var)] <- 'THQ'
    var[grepl('Blue Tongue', var)] <- 'THQ'
    var[grepl('Juice', var)] <- 'THQ'
    var[grepl('Kaos', var)] <- 'THQ'
    var[grepl('Paradigm', var)] <- 'THQ'
    var[grepl('Mass Media', var)] <- 'THQ'
    var[grepl('Helixe', var)] <- 'THQ'
    var[grepl('Locomotive', var)] <- 'THQ'
    var[grepl('Heavy Iron', var)] <- 'THQ'
    var[grepl('Incinerator', var)] <- 'THQ'
    var[grepl('Big Huge', var)] <- 'THQ'
    var[grepl('Nordic', var)] <- 'THQ'
    
    
    var[grepl('Konami', var)] <- 'Konami'
    var[grepl('Kojima', var)] <- 'Konami'
    
    
    var[grepl('Acclaim', var)] <- 'Disney'
    var[grepl('Disney', var)] <- 'Disney'
    var[grepl('Buena', var)] <- 'Disney'
    var[grepl('Propaganda', var)] <- 'Disney'
    var[grepl('TOYBOX', var)] <- 'Disney'
    
    
    var[grepl('Capcom', var)] <- 'Capcom'
    var[grepl('Blue Castle', var)] <- 'Capcom'
    
    
    
    
    var[!(var == 'EA' | var == 'SONY' | var == 'Nintendo' | 
              var == 'Microsoft' | var == 'Ubisoft' | var == 'Tencent'
          | var == 'Activision Blizzard' | var == 'Namco'
          | var == 'GungHo')] <- 'Other'
    
    return(var)
}
```

Needs more reasearch, later if we have time.

```{r}
games$Main_Developer <- filter_developer(games$Developer)
```




7. Game Developer country

```{r}
developer_country <- function(var) {
    var[var == 'EA' |
        var == 'Disney' | 
        var == 'SONY' |
        var == 'Microsoft' | 
        var == 'Activision Blizzard'] = 'US'
    
    var[var == 'Ubisoft'] = 'France'
    
    var[var == 'Nintendo' |
        var == 'Namco' | 
        var == 'GungHo'] = 'Japan'
    
    var[var == 'Tencent'] = 'China'
    
    return(var)
}
```

```{r}
games$Developer_Country <- developer_country(games$Main_Developer)
```




8. Publisher main company
```{r}
games$Main_Publisher <- filter_developer(games$Publisher)
```





#### Visual analysis of numerical variables:

We are mostly interested in global sales:
(We might want to explore which variables affect the global sales)
```{r}
games %>% 
    ggplot(aes(x = log(Global_Sales)))+
    geom_histogram(bins = 25, fill = 'deepskyblue2', col = 'blue') + 
    theme_light()
```

## Comments: since the original scale of global scales is not highly skewed to the right, we did log-transformation on it. For model assumptions: looks pretty good for MLR. 







Plot Global sales by region:
```{r}
sales <- melt(games[,c(6:9)])
names(sales) <- c('region', 'sales')

sales %>% ggplot(aes(x = log(sales))) + 
    geom_histogram(bins = 25, fill = 'deepskyblue2', col = 'blue') +
    facet_grid(.~ region)
```

Box-plots by region:
```{r}
sales %>% ggplot(aes(y = log(sales), x = region)) + 
    geom_boxplot(aes(fill = region)) + 
    theme_light()
```

## Comments: 
We would like to check if the sales differ significantly by region. There is no obvious heteroskedasticity. 




Global sales by genre:
```{r}
games %>% ggplot(aes(y = log(Global_Sales), x = Genre)) + 
    geom_boxplot(aes(fill = Genre)) + 
    theme_light() +
    theme(axis.text.x = element_blank())
```




Global sales by platform:

```{r}
games %>% ggplot(aes(y = log(Global_Sales), x = Platform_Gen)) + 
    geom_boxplot(aes(fill = Platform_Gen)) + 
    theme_light() +
    theme(axis.text.x = element_blank())
```

There are more than platforms, so it would be better to group them: Done



Global sales by platform developing companies:
```{r}
games %>% ggplot(aes(y = log(Global_Sales), x = Platform_Company)) + 
    geom_boxplot(aes(fill = Platform_Company)) + 
    theme_light() +
    theme(axis.text.x = element_blank())
```



Global sales by platform family:

```{r}
games %>% ggplot(aes(y = log(Global_Sales), x = Family_Platform)) + 
    geom_boxplot(aes(fill = Family_Platform)) + 
    theme_light() +
    theme(axis.text.x = element_blank())
```





Global sales by main developers:

```{r}
games %>% ggplot(aes(y = log(Global_Sales), x = Main_Developer)) + 
    geom_boxplot(aes(fill = Main_Developer)) + 
    theme_light() +
    theme(axis.text.x = element_blank())
```








## Analysis of numerical variables:

For EDA purposes only, fit their scatter plots and pairwise plots

1. Pairwise plots
```{r}
# choose only numeric variables
X <- games %>% 
    select(Global_Sales, Year_since_Release, Critic_Count, 
           Critic_Score, User_Count, User_Score) %>% 
    mutate_at(c('Global_Sales'), log) 
```

```{r}
pairs(X)
```

#### Comments: 
There are possible linear relationships between Global_Sales and Critic_Count, Critic_Score and User_Score. More detailed:

2. Critic_Score on Global_Sales
```{r}
plot(X$Critic_Score, X$Global_Sales, 
     xlab = 'Critic_Score', ylab = 'Global_Sales')
abline(lm(X$Global_Sales ~ X$Critic_Score), col = 'red')
```




3. User_Score on Global_Sales
```{r}
plot(X$User_Score, X$Global_Sales, 
     xlab = 'User_Score', ylab = 'Global_Sales')
abline(lm(X$Global_Sales ~ X$User_Score), col = 'red')
```



4. Global Sales by Critic_Count
```{r}
plot(X$Critic_Count, X$Global_Sales,
     xlab = 'Critic_Count', ylab = 'Global_Sales')
abline(lm(X$Global_Sales ~ X$Critic_Count), col = 'red')
```




5. Check for possible collinearity between numerical covariates:
```{r}
cor(X[,-1])
```

There is possible **collinearity** between Critic_Score and User_Score. If users give their scores after reviwing the critic score for that game, it's somehow biased and there is an obvious impact of critic score on the user score. This can be also checked by simple linear model fit:

```{r}
plot(X$Critic_Score, X$User_Score,
     xlab = 'Critic Score', ylab = 'User Score')
#fit without bias term (intercept)
abline(lm(X$User_Score ~ X$Critic_Score - 1), 
       col = 'red', lwd = 2)
```

```{r}
lm1 <- lm(X$User_Score ~ X$Critic_Score - 1)
lm1 %>% summary()
```

Fitting the linear model without an intercept results adjusted in R-square = 0.9683, which is a quite big amount. We can, further reveal if this possible collinearity if impacting the model fit in a bad way by analyzing the residual plots.




5. Did Global sales change by year?
```{r}
games %>% filter(Global_Sales < 60) %>% 
    ggplot(aes(x = as.factor(Year_of_Release), y = log(Global_Sales))) +
    geom_boxplot(fill = 'steelblue3', col = 'steelblue4') + 
    theme_light() +
    xlab('Year_of_Release') +
    theme(axis.text.x = element_text(angle = 90)) 
```

Significantly noticeable sales started in 1996, with 7 sales records in that year. Before 1996, there are only 4 records in 1985, 1988, 1991 and 1992. Visually there isn't much significant change in average global sales over time from 1996 to 2016. However, to be sure, we should run statistical tests in order sto ap/prove it.






## Melt variables

In order to include region as a new variable, we should melt sales by region:

```{r}
# exclude global sales, if you will need them, you can include them later:
sales <- melt(games[,c(-1, -10)], 
              measure.vars = c('NA_Sales', 'EU_Sales', 
                               'JP_Sales', 'Other_Sales'))
names(sales) <- c('Platform', 'Year_of_Release', 'Genre', 'Publisher',
                  'Critic_Score', 'Critic_Count', 'User_Score',
                  'User_Count', 'Developer', 'Rating', 'Year_since_Release',
                  'Decade', 'Platform_Company', 'Platform_Gen',
                  'Main_Developer', 'Developer_Country', 'Family_Platform',
                  'Main_Publisher', 'Region', 'Sales')

# write this variable into csv file
write.csv(games, 'games.csv', row.names = FALSE)

# write games variable into csv file
write.csv(sales, 'sales.csv', row.names = FALSE)
```





#### Interaction plots

1. Sales by Platform_Gen and Region
```{r}
# (!!!) before transforming the sales, add the minimum sales count for each 0 # value however, doesn't seem to be efficient 

#min_non_zer_sales <- min(sales$Sales[sales$Sales != 0])
#sales$Sales[sales$Sales == 0] <- min_non_zer_sales
```


```{r}
sales %>% ggplot(aes(y = log(Sales), x = Platform_Gen)) + 
    geom_boxplot(aes(fill = Platform_Gen)) + 
    facet_grid(.~Region) +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90))
```

##### Mosaic plot is already in Meltem's version




2. Sales by Platform_Company and Region
```{r}
sales %>% ggplot(aes(y = log(Sales), x = Platform_Company)) + 
    geom_boxplot(aes(fill = Platform_Company)) + 
    facet_grid(.~Region) +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90))
```



3. Sales by Family_Platform and Region
```{r}
sales %>% ggplot(aes(y = log(Sales), x = Family_Platform)) + 
    geom_boxplot(aes(fill = Family_Platform)) + 
    facet_grid(.~Region) +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90))
```



4. Sales by Genre and Region
```{r}
sales %>% ggplot(aes(y = log(Sales), x = Genre)) + 
    geom_boxplot(aes(fill = Genre)) + 
    facet_grid(.~Region) +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90))
```




5. Sales by Main_Developer and Region
```{r}
sales %>% ggplot(aes(y = log(Sales), x = Main_Developer)) + 
    geom_boxplot(aes(fill = Main_Developer)) + 
    facet_grid(.~Region) +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90))
```




6. Sales by Developer_Country and Region ??? makes sense???
```{r}
sales %>% ggplot(aes(y = log(Sales), x = Developer_Country)) + 
    geom_boxplot(aes(fill = Developer_Country)) + 
    facet_grid(.~Region) +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90))
```




7. Sales by Main_Developer and Platform_Compnany
```{r}
sales %>% ggplot(aes(y = log(Sales), x = Platform_Company)) + 
    geom_boxplot(aes(fill = Platform_Company)) + 
    facet_grid(.~Region) +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90))
```




8. Sales by Genre and Platform_Company
```{r}
sales %>% ggplot(aes(y = log(Sales), x = Genre)) + 
    geom_boxplot(aes(fill = Genre)) + 
    facet_grid(.~Platform_Company) +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90))
```




9. Sales by Genre and Main_Developer
```{r}
sales %>% ggplot(aes(y = log(Sales), x = Genre)) + 
    geom_boxplot(aes(fill = Genre)) + 
    facet_grid(.~Main_Developer) +
    theme_light() +
    theme(axis.text.x = element_blank())
```




10. Sales by Genre and Decade
```{r}
sales %>% ggplot(aes(y = log(Sales), x = Genre)) + 
    geom_boxplot(aes(fill = Genre)) + 
    facet_grid(.~Decade) +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90))
```


### Comments: We can keep all this example plots, so that we can choose *some* of them for our report later.







##. Independence of Categorical variables

```{r}

```


```{r}

```


```{r}

```

















