---
title: "MLR1-2 on nonzero dataset"
author: "Gulzina Kuttubekova, Meltem Ozcan"
date: "12/4/2019"
output:
  pdf_document: default
  word_document: default
---

```{r, include=FALSE}
library(dplyr)
library(ggplot2)
library(reshape)
library(gdata)
library(RColorBrewer)
library(visdat)
library(naniar)
library(inspectdf)
library(corrplot)
library(splitstackshape)
library(lmtest)
```


```{r}
games <- read.csv('games.csv')
sales <- read.csv('sales.csv')
```

```{r}
# log-transform and remove zeros
sales_nonzero <- sales %>% select_all() %>% 
    filter(Sales != 0) 
```


```{r}
set.seed(13)
sets <- stratified(sales_nonzero, c('Platform', 'Genre', 'Publisher',
                            'Developer', 'Rating', 'Decade',
                            'Platform_Company', 'Platform_Gen',
                            'Family_Platform', 'Main_Developer',
                            'Developer_Country', 'Main_Publisher',
                            'Region'), 0.7, bothSets = TRUE)

train_sales <- sets$SAMP1
test_sales <- sets$SAMP2
```


# MLR without interactions (for non-zero values)
```{r}
mlr_without_nonzero <- lm(log(Sales) ~ Genre + Critic_Score + Critic_Count +
                              Rating +
              Decade + Platform_Company + Platform_Gen + Family_Platform +
              Main_Developer + Main_Publisher + Region, 
              data = train_sales)
mlr_without_nonzero %>% summary()
```

```{r}
plot(mlr_without_nonzero)
```


# Check the real normality. On the 0.05 significance level, normality condition is still violated. But at least the Residual and QQ plots look nicer. 
```{r}
shapiro.test(mlr_without_nonzero$residuals
             [sample(1:length(train_sales$Platform),5000)])
```

However, heteroskedacticity is still present. 
```{r}
bptest(mlr_without_nonzero)
```

# get the AIC and BIC 
```{r}
AIC(mlr_without_nonzero)
BIC(mlr_without_nonzero)
```

```{r}
# rmse on train data
sqrt(sum((mlr_without_nonzero$fitted.values - train_sales$Sales)^2) /
         length(mlr_without_nonzero$fitted.values))


predicted_sales <- predict(mlr_without_nonzero,
                           test_sales[,-c(1,2,4,7,8,9,11,17,20)])

# rmse on test data
sqrt(sum((predicted_sales - test_sales$Sales)^2) / length(predicted_sales))
```






# MLR with interactions (for non-zero values)
```{r}
mlr_with_nonzero <-  lm(log(Sales) ~ Genre + Critic_Score + Critic_Count + Rating +
              Decade + Platform_Company + Platform_Gen + Family_Platform +
              Main_Developer + Main_Publisher + Region +
                  Genre:Region + Main_Developer:Region +
                  Main_Publisher:Region + Genre:Decade, 
              data = train_sales)
mlr_with_nonzero %>% summary()
```

```{r}
plot(mlr_with_nonzero)
```

# Check the real normality. On the 0.05 significance level, normality condition is still violated. But at least the Residual and QQ plots look nicer. 
```{r}
shapiro.test(mlr_with_nonzero$residuals
             [sample(1:length(train_sales$Platform),5000)])
```

However, heteroskedacticity is still present. 
```{r}
bptest(mlr_with_nonzero)
```

# get the AIC and BIC 
```{r}
AIC(mlr_with_nonzero)
BIC(mlr_with_nonzero)
```

```{r}
# rmse on train data
sqrt(sum((mlr_with_nonzero$fitted.values - train_sales$Sales)^2) /
         length(mlr_with_nonzero$fitted.values))


predicted_sales <- predict(mlr_with_nonzero,
                           test_sales[,-c(1,2,4,7,8,9,11,17,20)])

# rmse on test data
sqrt(sum((predicted_sales - test_sales$Sales)^2) / length(predicted_sales))
```























